\paragraph{NAME\label{NAME}\index{NAME}}


combineRank - calculates various Ranks for a Combine crawled database

\paragraph{SYNOPSIS\label{SYNOPSIS}\index{SYNOPSIS}}


combineRank  $<$action$>$ --jobname $<$name$>$ --verbose



where action can be one of PageRank, PageRankBL, NetLocRank, and
exportLinkGraph. Results on STDOUT.

\paragraph{OPTIONS AND ARGUMENTS\label{OPTIONS_AND_ARGUMENTS}\index{OPTIONS AND ARGUMENTS}}


jobname is used to find the appropriate configuration (mandatory)



verbose enables printing of ranks to STDOUT as SQL INSERT statements

\subparagraph*{Actions calculating variants of PageRank\label{Actions_calculating_variants_of_PageRank}\index{Actions calculating variants of PageRank}}
\begin{description}

\item[{PageRank}] \mbox{}

calculate standard PageRank


\item[{PageRankBL}] \mbox{}

calculate PageRanks with backlinks added for each link


\item[{NetLocRank}] \mbox{}

calculate SiteRank for each site and a local DocRank for documents within each site.
Global ranks are then calulated as SiteRank * DocRank

\end{description}
\subparagraph*{Actions exporting link data\label{Actions_exporting_link_data}\index{Actions exporting link data}}
\begin{description}

\item[{exportLinkGraph}] \mbox{}

export linkgraph from Combine database

\end{description}
\paragraph{DESCRIPTION\label{DESCRIPTION}\index{DESCRIPTION}}


Implements calculation of different variants of PageRank.



Results are written to STDOUT and can be huge for large databases.



Linkgraph is exported in ASCII as a sparse matrix, one row per line.
First integer is the ID (urlid) of a page with links. The rest of
integers on the line are IDs for pages linked to. Ie
121 5624 23416 51423 267178
means that page 121 links to pages 5624 23416 51423 267178

\paragraph{EXAMPLES\label{EXAMPLES}\index{EXAMPLES}}
\begin{description}

\item[{\texttt{combineRank --jobname aatest --verbose PageRankBL}}] \mbox{}

calculate PageRank with backlinks, result on STDOUT


\item[{\texttt{combineRank --jobname aatest --verbose exportLinkGraph}}] \mbox{}

export the linkgraph to STDOUT

\end{description}
\paragraph{SEE ALSO\label{SEE_ALSO}\index{SEE ALSO}}


combine



Combine configuration documentation in \emph{/usr/share/doc/combine/}.

\paragraph{AUTHOR\label{AUTHOR}\index{AUTHOR}}


Anders Ardö, $<$anders.ardo@it.lth.se$>$

\paragraph{COPYRIGHT AND LICENSE\label{COPYRIGHT_AND_LICENSE}\index{COPYRIGHT AND LICENSE}}


Copyright (C) 2006 Anders Ardö



This library is free software; you can redistribute it and/or modify
it under the same terms as Perl itself, either Perl version 5.8.4 or,
at your option, any later version of Perl 5 you may have available.



See the file LICENCE included in the distribution at
 \textsf{http://combine.it.lth.se/}

